Курсовая работа по теме \\ \Huge{«Методы оптимизации»}

### 2008-12-18 simplex-method.tkz.tex
Use smaller circle nodes to mark points

      % Pins for solutions on each step
      \draw node[circle, fill=black, scale=0.5, every pin edge/.style={draw=black, line width=2pt},
                 pin={right:\contour{white}{$(2, 3.5)$}}] at (axis cs:2,3.5) {};
      \draw node[circle, fill=black, scale=0.5, 
                 pin={left:$(0, 2)$}] at (axis cs:0,2) {};

>>>>

      % Pins for solutions on each step
      \draw node[circle, fill=black, scale=0.25, every pin edge/.style={draw=black, line width=2pt},
                 pin={right:\contour{white}{$(2, 3.5)$}}] at (axis cs:2,3.5) {};
      \draw node[circle, fill=black, scale=0.25, 
                 pin={left:$(0, 2)$}] at (axis cs:0,2) {};
